---
title: "introduction"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{introduction}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

The goal of **ssrn** is to implement the algorithm provided in "*Scan for estimating the transmission route of COVID-19 on railway network using passenger volume*". It is a generalization of the scan statistic approach for railway network to identify the hot railway route for transmitting infectious diseases.

Below are some of the features of the package, using the built-in dataset (a section of JR's Tokaido Line).

```{r, eval = TRUE, echo = TRUE, message = FALSE}
library(ssrn)
library(scanstatistics)
library(dplyr)
data("jreast_jt", package = "ssrn")
```

`jreast_jt` includes the code and names of stations between Tokyo and Yugawara.

```{r, eval = TRUE}
glimpse(jreast_jt)
glimpse(jreast_jt_od)
```

## Create network window zones

Prepare a matrix object to detect hotspots from spatial relationships on the railway. This package provides auxiliary functions that create these matrices based on the data indicating the relationship between stations (the order of stops) and the passenger volumes.

- Make an adjacency matrix of stations with `make_adjacency_matrix()`.
- Create a distance matrix with `make_passenger_matrix()` based on the passenger volumes.

```{r, eval = TRUE}
adj <- 
  make_adjacency_matrix(jreast_jt,
                        st_code, next_st_code)
dist <- 
  jreast_jt_od %>%
  make_passenger_matrix(jreast_jt,
                        departure_st_code,
                        arrive_st_code,
                        st_code,
                        volume)
```

```{r, eval = TRUE, results = "hide"}
zones <- 
  network_window(adj, 
                 dist, 
                 type = "connected_B", 
                 cluster_max = 20)
```

```{r, eval = FALSE, echo = TRUE}
zones
#> [[1]]
#> [1] 1
#> 
#> [[2]]
#> [1] 1 2
#> 
#> [[3]]
#> [1] 1 2 3
#> 
#> [[4]]
#> [1] 1 2 3 4
#> ...
#> [[134]]
#> [1] 20
```

## Estimate hot railway route

Apply the method of spatial scan statistics based on the zone.

```{r}
counts <-
  c(2, 2, 1, 5, 7, 1, 
    1, 1, 1, 1, 2, 2, 
    5, 4, 7, 5, 1, 2, 
    1, 1) %>% 
  purrr::set_names(
    jreast_jt$st_name)
counts

poisson_result <-
  scan_eb_poisson(counts = counts,
                  zones = zones,
                  baselines = rep(1, 20),
                  n_mcsim = 10000,
                  max_only = FALSE)
```

```{r}
top <- top_clusters(poisson_result,
                   zones,
                   k = 2,
                   overlapping = FALSE)
detect_zones <- 
  top$zone %>%
  purrr::map(get_zone, zones = zones) %>%
  purrr::map(function(x) jreast_jt$st_name[x])
df_zones <-
  seq_len(length(detect_zones)) %>%
  purrr::map_df(
    ~ tibble::tibble(
      cluster = .x,
      st_name = detect_zones[.x]
    )
  ) %>%
  tidyr::unnest(cols = st_name)
df_zones
```
